FIXME

### 2013-09-09 writeups/proposal/proposal.tex
Mon commits
Former-commit-id: 0c1101609063f328d4a56e111b18fd615384cf26 [formerly 993e3e5e6f2061eea359b90ba771ed678c029624]
Former-commit-id: d118d6bf9eb0594f02316cf3bbf709256dfada58

% FIXME: Fix cite for Bauer2012
One traditional technique is to provide the user with a powerful search engine so that they can actively look for content that interests them.
However, users are not forming the same search queries that work so effectively on search engines like Google.
Users of social media sites are searching for information that is happening now, in real time \parencite{Bauer2012}.
In other words, users on social-media sites want the fresh \emph{stream} of information about a particular topic.
This can certainly be seen in the main user-interface views that these social media site provide:
Twitter's homepage showing your followers' tweets, Facebook's homepage showing your friends' posts, StackOverflow's daily digest of posts for particular tags, etc.

@@

FIXME: It is certainly the case that real-time search on these social media sites is growing \parencite{Jansen2011}.

@@

@@

\subsubsection{Random Permutations}

@@

With random permutations, each word environment vector is a large sparse vector of zeros with a few $[1,-1]$s in random locations. 
In order to create a new environment vector for a word that preceded another word in a sentence, that word's environment vector is bit shifted to the left one position.
This produces a new environment vector for the combination of the word and the position that is uncorrelated with the original word's environment vector and all other environment vectors.

@@

A retrieval for a word following ``stack'' (``stack $\Phi$'') is done by creating a memory vector out of all information in context.
In this case, assume only a single piece of order information is available, that ``stack'' precedes the word to retrieve.
So the memory vector for context is the environment vector for one-back ``stack'' ($m_{context} = e_{stack^{-1}}$).
The memory vector for ``overflow'' will be correlated the highest with this context vector since ``overflow'' contains this vector.

@@

Two models will be evaluated for hashtag prediction on both the Twitter and StackOverflow datasets:
A vector-based model and Bayesian retrieval model.
The random permutation model described in \textcite{Sahlgren2008} will be used for the vector-based model, since it has shown to perform better than the BEAGLE model \parencite{Recchia2010}.
The modified ACT-R Bayesian model described in \textcite{Stanley2013} will be used for the Bayesian model, since it has already been applied to tag use on StackOverflow posts.

\subsubsection{ACT-R Bayesian Model}

\begin{table}[!ht]
  \caption{Random Permutation Model}
  \label{tabRandPermModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Activation &		$A_{i} = r(m_{C},m_{i})$ \\
      Memory Vector &		$m_{i} = e_{i} + \sum_{j \in all past} c_{j} + \sum_{j \in all past} \sum_{k \in locations} o_{j,k}$ \\
      Unordered Context &	$c_{i} = e_{i}$ \\
      Ordered Context &		$o_{i,k} = e_{i^{-k}}$ \\
      Context Memory Vector &	$m_{C} = \sum_{j \in C} c_{j} + \sum_{j \in C} \sum_{j \in locations} o_{j,k}$ \\
      Environment Vector & 	$e_{i} = rand$ \\
      \hline
    \end{tabu}
  }
\end{table}

A formal description of the random permutation model in \textcite{Sahlgren2008} is included in Table \ref{tabRandPermModel}.

TODO: Formal description of each model.

>>>>

% FIXME: Fix cite for Bauer2012
One traditional technique is to provide the user with a powerful search engine so that they can actively look for content that interests them.
However, users are not forming the same search queries that work so effectively on search engines like Google.
A growing number of users on social media sites are searching for information that is happening now, in real time \parencites{Bauer2012,Jansen2011}.
In other words, users on social-media sites want the fresh \emph{stream} of information about a particular topic.
This can certainly be seen in the main user-interface views that these social media site provide:
Twitter's homepage showing your followers' tweets, Facebook's homepage showing your friends' posts, StackOverflow's daily digest of posts for particular tags, etc.

@@

@@

\subsubsection{\textcite{Stanley2013}'s ACT-R DM Model for StackOverflow}

@@

@@

\begin{table}[!ht]
  \caption{Random Permutation Model}
  \label{tabRandPermModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Activation &		$A_{i} = r(m_{C},m_{i})$ \\
      Memory Vector &		$m_{i} = \sum_{i \in all past} c_{i} + \sum_{i \in all past} \sum_{l \in locations} o_{i,l}$ \\
      Unordered Context &	$c_{i} = e_{i}$ \\
      Ordered Context &		$o_{i,l} = e_{i^{-l}}$ \\
      Context Memory Vector &	$m_{C} = \sum_{i \in C} c_{i} + \sum_{i \in C} \sum_{l \in locations} o_{i,l}$ \\
      Environment Vector & 	$e_{i} = rand$ \\
      \hline
    \end{tabu}
  }
\end{table}

A formal description of the random permutation model in \textcite{Sahlgren2008} is included in Table \ref{tabRandPermModel}.
With random permutations, each word environment vector ($e_{i}$) is a large sparse vector of zeros with a few $[1,-1]$s in random locations. 
In order to create a new environment vector for a word that preceded another word in a sentence, that word's environment vector ($e_{i}$) is bit shifted to the left one position ($^{-1}$).
This produces a new environment vector ($e_{i^{-1}}$) for the combination of the word and the position that is uncorrelated with the original word's environment vector and all other environment vectors.

@@

A retrieval for a word following ``stack'' (``stack $\Phi$'') is done by creating a memory vector out of all information in context.
In this case, assume only a single piece of order information is available, that ``stack'' precedes the word to retrieve.
So the memory vector for context is the environment vector for one-back ``stack'' ($m_{C} = e_{stack^{-1}}$).
The memory vector for ``overflow'' ($m_{overflow}$) will be correlated the highest with this context vector ($m_{C}$) since ``overflow'' contains this vector.

@@

Two models will be evaluated for hashtag prediction on both the Twitter and StackOverflow datasets:
A vector-based model and Bayesian retrieval model.
The random permutation model \parencite{Sahlgren2008} in Table \ref{tabRandPermModel} will be used for the vector-based model, since it has shown to perform better than the BEAGLE model \parencite{Recchia2010}.
The modified ACT-R Bayesian model \parencite{Stanley2013} in Table \ref{tabModACTRMOdel} will be used for the Bayesian model, since it has already been applied to tag use on StackOverflow posts.

These models will be the starting point for modeling tag use on the Twitter and StackOverflow sites.
The models may be modified during testing if the data indicate that slight modifications are needed to improve model performance.
Also there are planned modifications to each model as part of the research:
incorporating user prior information into the vector-based model, and incorporating word order information into the Bayesian model.
